---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# issue

Create a simple human readable table for readme that displays status of GitHub repositoy issues

## Installation

You can install issue from github with:

```{r gh-installation, eval = FALSE}
# install.packages("remotes")
remotes::install_github("yonicd/issue")
```

## Prerequisites

This package relies heavily on the querying the GitHub API. You can create a personal access token (PAT) in `R` with [usethis](https://usethis.r-lib.org/reference/browse_github_pat.html). 

```{r}
library(issue)
```

```{r example}
raw_data <- issue::get_issues(
  repo = 'r-lib/pkgdown',
  last = 20,
  PAT  = Sys.getenv('GITHUB_PAT')
  )

tbl <- raw_data%>%
  issue::issue_tibble()

x <- tbl%>%
  issue::md_table()
```

## Current Issues

```{r,results='asis',echo=FALSE}
x[c(1:5),]%>%
  knitr::kable()
```

<details><summary>View More</summary>

```{r,results='asis',echo=FALSE}
x[-c(1:5),]%>%
  knitr::kable()
```

</details>
<br>

## For Developers

The `issue_tibble` has all kinds of useful information for developers to interrogate either their own repository or other repositories directly from `R`.

```{r}
tbl%>%
  dplyr::glimpse()
```

```{r}
tbl$comments_users[[1]]%>%
  dplyr::glimpse()
```

```{r}
tbl$comments_users[[1]]$user[[1]]%>%
  tibble::as.tibble()%>%
  dplyr::glimpse()
```